---
title: "PCS Dashboard Data Preparation"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

```

```{r}
cat("\014")  # clears console
rm(list = ls())  # clears global environment
try(dev.off(dev.list()["RStudioGD"]), silent = TRUE) # clears plots
try(p_unload(p_loaded(), character.only = TRUE), silent = TRUE) # clears packages
options(scipen = 100) # disables scientific notion for entire R session
```



# PCS User Inputs!

If you create an R project that contains the files below, do not change anything. If you do not, input a filepath to your TOC and check-in data within the quotation marks below.

```{r}

check_in_path <-  "iPad_check_in_data.csv"

TOC_path <-  "insightly_TOC_report.csv"

all_contacts_path <- 'all_contacts.csv'

TOC_file_out <-  "TOC_tableau_ready.csv"

iPad_file_out <- "iPad_tableau_ready.csv"

Ogranizational_file_out <- "Org_tableau_ready.csv"
```


This is a list of categories of interest. These will be used to get counts from the iPad check in data. If a new activity is added that you want to count, add it, in quotes, to the list below.

```{r}
cat_of_int <- c("volunteer", "squash", "fitness", "cafestudy", "event")
```

Below are the goals set for each of the organisational level milestone.
- Guided and self guided milestone goals represent % Access.
- Equity and cohesion represent raw number of respective milestones achieved.

```{r}
guided_access_milestone_goal <- 80

sg_access_milestone_goal <- 30

equity_milestone_goal <- 20

cohesion_milestone_goal <- 10
```


# Imports



```{r}
library(pacman)
p_load(dplyr)
p_load(ggplot2)
p_load(tidyverse)
p_load(janitor)
p_load(lubridate)
p_load(scales)
p_load(skimr)

ipad_df <- read_csv(check_in_path)

toc <- read_csv(TOC_path)

all_contacts <- read_csv(all_contacts_path)
```



# ToC

```{r}
toc <- clean_names(toc)
ipad_df <- clean_names(ipad_df)

# Change 1 member_since 2008 to 2018
toc$membership_start_date <- ifelse(toc$membership_start_date == "2008", "2018",
                                    toc$membership_start_date)

#2. Combine 2 "non-binary responses"

toc <- toc |> mutate(
  gender = ifelse(gender == "Non-Binary", "Non-binary", gender)
)


#3. Splitting columns

#a. Membership Type - Access & Dependent Status
```


```{r}
# CODE for isolating access status:
# Splitting membership column

# No missing data in membership
sum(is.na(toc$membership))

# Pulling out membership type
toc_cleaned <- toc |> separate(membership, 
                               into = c("member_type", "other_stuff"), 
                               sep = "-", extra = "merge")

# Pulling out access status
toc_cleaned <- toc_cleaned |> 
  mutate(access_member = str_extract(other_stuff, "Access"))

# Pulling out dependent status
toc_cleaned <- toc_cleaned |> separate(other_stuff, 
                                       into = c("dependent_status", "access_status"), 
                                       sep = "(Access)(?=\\s|$)")

# Drop "acesss_status column
toc_cleaned <- toc_cleaned |> select(-access_status)


# Report access as "Missing" if membership was canceled
# Allows us to isolate which current members are actually access members
toc_cleaned <- toc_cleaned |> mutate(
  access = if_else(member_type == "Canceled", "Missing", "Not Missing")
)

# Translate access values to account for access, non-access, or missing/cancelled data
toc_cleaned <- toc_cleaned |> mutate(
  access = case_when(
    access_member == "Access" ~ "Access",
    access == "Missing" ~ NA, 
    TRUE ~ "Not Access"
  )
)

# Verify results
table(toc_cleaned$access)    
sum(is.na(toc$membership))

# Drop "acesss_member" column
toc_cleaned <- toc_cleaned |> select(-access_member)
```



```{r}
# Code for Dependent Status

############# Dependent Status Column ##########################################

# Report dependent status as "Missing" if member status was missing
toc_cleaned <- toc_cleaned |> mutate(
  dependent = if_else(member_type == "Canceled", "Missing", "Not Missing"))

#Replace dashed entries with non-dashed
toc_cleaned <- toc_cleaned |> mutate(dependent_status =
                                       gsub("Dependent -", "Dependent", dependent_status))

toc_cleaned <- toc_cleaned |> mutate(dependent_status = gsub("Partner -", "Partner", dependent_status))

#table(test$dependent_status)
#unique(test$dependent_status)

toc_cleaned <- toc_cleaned |> mutate(
  shared_membership = case_when(
    dependent_status == " Dependent" ~ "Dependent",
    dependent_status == " Dependent " ~ "Dependent",
    dependent_status == " Partner" ~ "Partner",
    dependent_status == " Partner " ~ "Partner",
    dependent == "Missing" ~ NA,
    TRUE ~ "Not Shared Membership"
  )
)

# Drop dependent column
toc_cleaned <- toc_cleaned |> select(-dependent)
toc_cleaned <- toc_cleaned |> select(-dependent_status)
```

Breaking Apart TOC elements

```{r}
###############################################################################

#Breaking Apart Theory of Change Elements

unique(toc_cleaned$theory_of_change)

toc_cleaned$toc_rally_portland <- ifelse(grepl("Rally Portland", 
                                           toc_cleaned$theory_of_change, 
                                           ignore.case = TRUE), "Yes", "No")

toc_cleaned$toc_camp_fish_hawk <- ifelse(grepl("Camp Fish Hawk", 
                                           toc_cleaned$theory_of_change, 
                                           ignore.case = TRUE), "Yes", "No")

toc_cleaned$guided_opportunities <- ifelse(grepl("Guided Opportunities", 
                                                 toc_cleaned$theory_of_change,
                                                 ignore.case = TRUE), "Yes", "No")

toc_cleaned$guided_integration <- ifelse(grepl("Guided Integration", 
                                               toc_cleaned$theory_of_change, 
                                               ignore.case = TRUE), "Yes", "No")

toc_cleaned$guided_wellness <- ifelse(grepl("Guided Wellness", 
                                            toc_cleaned$theory_of_change, 
                                            ignore.case = TRUE), "Yes", "No")

toc_cleaned$equity <- ifelse(grepl("Equity", 
                                   toc_cleaned$theory_of_change,
                                   ignore.case = TRUE), "Yes", "No")

toc_cleaned$events <- ifelse(grepl("Events", 
                                   toc_cleaned$theory_of_change, 
                                   ignore.case = TRUE), "Yes", "No")

toc_cleaned$wellness <- ifelse(grepl("Wellness", 
                                     toc_cleaned$theory_of_change, 
                                     ignore.case = TRUE), "Yes", "No")

toc_cleaned$squash <- ifelse(grepl("Squash", 
                                   toc_cleaned$theory_of_change,
                                   ignore.case = TRUE), "Yes", "No")

toc_cleaned$volunteering <- ifelse(grepl("Volunteering", 
                                         toc_cleaned$theory_of_change,
                                         ignore.case = TRUE), "Yes", "No")

toc_cleaned$family_squash_clinics <- ifelse(grepl("Family Squash", 
                                                  toc_cleaned$theory_of_change, 
                                                  ignore.case = TRUE), "Yes", "No")

toc_cleaned$advisor <- ifelse(grepl("Advisor", 
                                    toc_cleaned$theory_of_change, 
                                    ignore.case = TRUE), "Yes", "No")

toc_cleaned$self_guided_opportunities <- ifelse(grepl("Self-Guided Opportunities", 
                                                      toc_cleaned$theory_of_change,
                                                      ignore.case = TRUE), "Yes", "No")

toc_cleaned$self_guided_wellness <- ifelse(grepl("Self-Guided Wellness", 
                                                 toc_cleaned$theory_of_change,
                                                 ignore.case = TRUE), "Yes", "No")

toc_cleaned$self_guided_integration <- ifelse(grepl("Self-Guided Integration", 
                                                    toc_cleaned$theory_of_change, 
                                                    ignore.case = TRUE), "Yes", "No")

toc_cleaned$cohesion <- ifelse(grepl("Cohesion", 
                                     toc_cleaned$theory_of_change, 
                                     ignore.case = TRUE), "Yes", "No")

toc_cleaned$toc_farm_team <- ifelse(grepl("Farm Team", 
                                      toc_cleaned$theory_of_change, 
                                      ignore.case = TRUE), "Yes", "No")

toc_cleaned$cafe_study <- ifelse(grepl("Cafe/Study", 
                                       toc_cleaned$theory_of_change,
                                       ignore.case = TRUE), "Yes", "No")

toc_cleaned$guided_phase <- ifelse(grepl("Guided Phase", 
                                         toc_cleaned$theory_of_change, 
                                         ignore.case = TRUE), "Yes", "No")

toc_cleaned$challenge <- ifelse(grepl("Challenge", 
                                      toc_cleaned$theory_of_change,
                                      ignore.case = TRUE), "Yes", "No")

toc_cleaned$access_toc <- ifelse(grepl("Access", 
                                       toc_cleaned$theory_of_change,
                                       ignore.case = TRUE), "Yes", "No")

###
```


Separate racial background data from list to one column per list item
```{r}
#Breaking Apart Race/Ethnicity

toc_cleaned <- toc_cleaned |> separate(race_ethnicity, 
                                       into = c("Race1", "Race2"), sep = ";", 
                                       extra = "merge", remove = FALSE)

```


Total TOC Column Entries:
```{r}
# Get total # of TOC activities

toc_cleaned <- toc_cleaned |> mutate(toc_total = rowSums(toc_cleaned == "Yes",
                                                         na.rm = TRUE))

# Creating yes/no binary columns for participation of programs for ToC 
#  milestones from season record 

toc_record_reconciled <- toc_cleaned %>% 
  mutate(
    record_rp = case_when(grepl("RP", season_record, ignore.case = TRUE) ~ "Yes", .default = "No"),
    record_farm = case_when(grepl("FarmTeam", season_record, ignore.case = TRUE) ~ "Yes", .default = "No"),
    record_camp = case_when(grepl("Summer", season_record, ignore.case = TRUE) ~ "Yes", .default = "No"),
    rp_match = case_when(toc_rally_portland == record_rp ~ "Yes", .default = "No"),
    farm_match = case_when(toc_farm_team == record_farm ~ "Yes", .default = "No"),
    camp_match = case_when(toc_camp_fish_hawk == record_camp ~ "Yes", .default = "No")
  ) %>% 
  select(contact_id, theory_of_change, season_record, toc_rally_portland, record_rp, rp_match, toc_farm_team, record_farm, farm_match, toc_camp_fish_hawk, record_camp, camp_match) 
  


toc_cleaned_v2 <- toc_cleaned %>% 
  mutate(
    record_rp = case_when(grepl("RP", season_record, ignore.case = TRUE) ~ "Yes", .default = "No"),
    record_farm = case_when(grepl("FarmTeam", season_record, ignore.case = TRUE) ~ "Yes", .default = "No"),
    record_camp = case_when(grepl("Summer", season_record, ignore.case = TRUE) ~ "Yes", .default = "No")
  )
  


toc_cleaned_v2 <- toc_cleaned_v2 %>% 
  mutate(
    camp_fish_hawk = case_when(toc_camp_fish_hawk == "Yes" | record_camp == "Yes" ~ "Yes", .default = "No"),
    farm_team = case_when(toc_farm_team == "Yes" | record_farm == "Yes" ~ "Yes", .default = "No"),
    rally_portland = case_when(toc_rally_portland == "Yes" | record_rp == "Yes" ~ "Yes", .default = "No")
  )

season_part <- toc_cleaned_v2 %>% 
  filter(!is.na(season_record))


season_part <- season_part %>% 
  rename("record" = "season_record") %>% 
  rename("id" = "contact_id")

season_part <- season_part %>% 
  select(id, record)
```

Records were broken down into separate rows, one per record, separated by a semicolon.

```{r}
season_part <- season_part %>% 
  separate_rows(record, sep = ';')
```


To clean data, records containing "23SpringFarmTeam" were converted to "22-23SpringFarmTeam" to amintain consistency in nomenclature, then the year, season, and program were separated into three separate columns.

```{r}
season_part_clean <- season_part %>% 
  mutate(record = replace(record, record == "23SpringFarmTeam", "22-23SpringFarmTeam")) %>% 
  mutate(year = str_extract(record, "[0-9-]+")) %>% 
  mutate(season = str_extract(record, "(Winter|Spring|Summer|Fall)")) %>% 
  mutate(program = str_extract(record, "(CIT|JSL|RP|Learningworks|LearningWorks|FarmTeam)"))
```


As some records in the data set contained a semicolon at the beginning of the list, this created some rows with blanks in the record. As these blanks did not represent anything they were removed.

The only program offered by PCS in the summer specifically is the camp, and every record that contained summer in the season contained an NA in the program, the assumption was made that all "Summer" season records were for camp, and the programs column was populated as such.


```{r}
season_part_clean <- season_part_clean[!(season_part_clean$record ==""), ]

season_part_clean <- season_part_clean %>% 
  mutate(program = case_when(
    season == "Summer" ~ "Camp",
    .default = as.character(program)
  ))

season_part_clean <- season_part_clean %>% 
  mutate(program = case_when(
    program == "Learningworks" ~ "LearningWorks",
    .default = as.character(program)
  ))
```


Made a new column combining year and season

```{r}
season_part_clean <- season_part_clean %>% 
  unite(year_season, year:season, sep = "", remove = FALSE, na.rm = TRUE)
```



As most of the date information is stored in terms of school year (i.e. 20-21), a year column was constructed by extractig a string from the school_year column based on the season (21-22Fall -> 21, as Fall is in the first half of the school year). If no season was given year was determined by the first number in the school year, similar to Fall.

```{r}
season_part_clean <- season_part_clean %>% 
  rename(school_year  = year) %>% 
  mutate(year = case_when(
    season == "Fall" ~ str_extract(school_year, "[^-]+"),
    season == "Winter" ~ str_extract(school_year, "(?<=-).*"),
    season == "Spring" ~ str_extract(school_year, "(?<=-).*"),
    is.na(season) ~ str_extract(school_year, "[^-]+"),
    .default = as.character(school_year)
  ))
```

Iterating through the data to pull out the latest year for each of the guided ToC milestones

```{r}
rp_latest_yr <- season_part_clean %>% 
  group_by(id, program) %>% 
  summarise(latest_yr = max(year)) %>% 
  filter(program == "RP")

camp_latest_yr <- season_part_clean %>% 
  group_by(id, program) %>% 
  summarise(latest_yr = max(year)) %>% 
  filter(program == "Camp")

farm_latest_yr <- season_part_clean %>% 
  group_by(id, program) %>% 
  summarise(latest_yr = max(year)) %>% 
  filter(program == "FarmTeam")
```


Adding the 'latest_year' for each activity
```{r}
rp_latest_yr <- rp_latest_yr %>% 
  select(id, latest_yr) %>% 
  rename(rally_portland_latest_year = latest_yr)

camp_latest_yr <- camp_latest_yr %>% 
  select(id, latest_yr) %>% 
  rename(camp_latest_year = latest_yr)

farm_latest_yr <- farm_latest_yr %>% 
  select(id, latest_yr) %>% 
  rename(farm_team_latest_year = latest_yr)

```

Joining the 'latest_year' to the theory of change data
```{r}
toc_cleaned_v3 <- left_join(
  toc_cleaned_v2,
  rp_latest_yr,
  by = join_by(contact_id == id)
)

toc_cleaned_v3 <- left_join(
  toc_cleaned_v3,
  camp_latest_yr,
  by = join_by(contact_id == id)
)

toc_cleaned_v3 <- left_join(
  toc_cleaned_v3,
  farm_latest_yr,
  by = join_by(contact_id == id)
)
```





```{r}
toc_cleaned_v3 <- toc_cleaned_v3 %>% 
  unite(full_name, first_name, last_name, sep = " ", remove = FALSE)

TOC_tableau_ready <- toc_cleaned_v3

```


# iPad Check-in 


data preparation

```{r}
# Remove unused columns and clean names
columns_to_remove <- c('type1', 'number1', 'number2', 'binary1', 'binary2', 'number3')
ipad_df <- ipad_df[, !names(ipad_df) %in% columns_to_remove]

ipad_df <- clean_names(ipad_df)
head(ipad_df)
```


The NAs in 'first_name' and 'last_name' do not matter since we have full of record_id (Customer's ID)

```{r}
# notice other types of NAs: #N/A
# Replace "#N/A" with actual NA values
ipad_df <- ipad_df |> mutate_all(function(x) gsub("#N/A", NA, x))

# Check for missing values in each column
colSums(is.na(ipad_df))

```

In this part, we wanted to break down the "date' column into separate columns with deeper information in 'Day of Week', 'Day', 'Month', 'Year' to find time - season patterns

```{r}
# Convert the 'date' column to datetime format
ipad_df$date <- as.POSIXct(ipad_df$date, format = "%m/%d/%Y %H:%M")

# Break down into separate columns
ipad_df <- ipad_df |> 
  mutate(day_of_week = wday(date, label = TRUE, abbr = FALSE),
         day = day(date),
         month = month(date, label = TRUE, abbr = FALSE),
         year = year(date),
         hour = as.POSIXct(format(date, format = "%H:%M"), format = "%H:%M"))

# Round the hour of the 'time' column
ipad_df$hour <- floor_date(ipad_df$hour, unit = "hour")

# Keep only the 'hour' in the 'time' column
ipad_df$hour <- format(ipad_df$hour, format = "%H")

head(ipad_df)

```

```{r}
# drop the 'first_name' and 'last_name' columns
ipad_df <- select(ipad_df, -first_name, -last_name )
head(ipad_df)
```
```{r}
# rename columns and add more timestamp
ipad_df_clean <- ipad_df |> rename(datetime = date)

ipad_df_clean <- ipad_df_clean |>  
  mutate(
    date = date(datetime),
    time = strftime(datetime, format = "%H:%M:%S"),
    time = hms::as_hms(time)
  )

head(ipad_df_clean)
```
In this section we are joining the "all_contacts" to the iPad check in data
```{r}
# change datatype to prepare for merging data
all_contacts$RecordId <- as.character(all_contacts$RecordId)

# merge info of 'first_name' and 'last_name' from the Contact file
ipad_df_clean <- left_join(ipad_df_clean, all_contacts, by = join_by(record_id == RecordId))
head(ipad_df_clean)
```

In this section we are combining 'orgvolunteer', 'volworkshift' and 'youthvolunteer' and replacing them with 'volunteer' in the 'category' column.

Then we are going to iterate through 'cat_of_int' and keep only activities found in that list, everything else will be converted to 'other'.
```{r}
ipad_df_clean <- ipad_df_clean |> 
  mutate(category = ifelse(category %in% c('orgvolunteer', 'volworkshift', 'youthvolunteer'), 'volunteer', category))


ipad_df_clean <- ipad_df_clean %>% 
  mutate(category = ifelse(category %in% cat_of_int, category, 'other'))

```

```{r}
ipad_tableau_ready <- ipad_df_clean
```



# Org A'



```{r}
toc_cleaned_v3
```


```{r}
ipad_df_clean
```
 Finding the minimum year using the lowest year available in the iPad checkin data.
```{r}
min_year <- min(year(ipad_df_clean$date))
```

```{r}
min_year
```


Creating a 'year_half' variable based on month, with Jan-Jun receiving 1, and Jul-Dec recieving 2
```{r}
ipad <- ipad_df_clean %>% 
  mutate(year_half = case_when(month(date) >= 1 & (month(date) <= 6) ~1, 
                               month(date) >= 7 & (month(date) <= 12) ~2,
                               .default = NA))
```


Getting counts by member per activity per 'year_half'

```{r}
biannual_activity_count <- ipad %>%
  filter(category == cat_of_int) %>% 
  group_by(
    year = year,
    year_half,
    record_id,
    category
  ) %>% 
  summarize(count = n()) %>% 
  pivot_wider(names_from = c(category), values_from = count) %>% 
  replace(is.na(.), 0)
```


```{r}
biannual_activity_count
```

renaming columns for activities
```{r}
biannual_activity_count <- biannual_activity_count %>% 
  rename(contact_id = record_id, squash_visits = squash, fitness_visits = fitness,
         event_visits = event, cafestudy_visits = cafestudy, volworkshift_visits = volunteer,)
```



Isolating season record for guided activities
```{r}
season_part2 <- toc_cleaned_v3 %>% 
  select(contact_id, season_record)
```


Cleaning and splitting season record


```{r}
season_part2 <- season_part2 %>% 
  rename("record" = "season_record") %>% 
  rename("id" = "contact_id")
```


```{r}
season_part2
```

Records were broken down into separate rows, one per record, separated by a semicolon.

```{r}
season_part2 <- season_part2 %>% 
  separate_rows(record, sep = ';')
```

```{r}
season_part2 %>% 
  distinct(record) %>% 
  arrange(desc(record))
```

```{r}
guide_programs_of_int <- c("RP", "JSL", "Camp", "Farm Team")
```



To clean data, records containing "23SpringFarmTeam" were converted to "22-23SpringFarmTeam" to amintain consistency in nomenclature, then the year, season, and program were separated into three separate columns.

```{r}
season_part_clean2 <- season_part2 %>% 
  mutate(record = replace(record, record == "23SpringFarmTeam", "22-23SpringFarmTeam")) %>% 
  mutate(year = str_extract(record, "[0-9-]+")) %>% 
  mutate(season = str_extract(record, "(Winter|Spring|Summer|Fall)")) %>% 
  mutate(program = str_extract(record, "(CIT|JSL|RP|Learningworks|LearningWorks|FarmTeam)"))
```


As some records in the data set contained a semicolon at the beginning of the list, this created some rows with blanks in the record. As these blanks did not represent anything they were removed.

```{r}
season_part_clean2 <- season_part_clean2[!(season_part_clean2$record ==""), ]
```



The only program offered by PCS in the summer specifically is the camp, and every record that contained summer in the season contained an NA in the program, the assumption was made that all "Summer" season records were for camp, and the programs column was populated as such.

```{r}
season_part_clean2 <- season_part_clean2 %>% 
  mutate(program = case_when(
    season == "Summer" ~ "Camp",
    .default = as.character(program)
  ))
```

```{r}
season_part_clean2 <- season_part_clean2 %>% 
  mutate(program = case_when(
    program == "Learningworks" ~ "LearningWorks",
    .default = as.character(program)
  ))
```


Made a new column combining year and season

```{r}
season_part_clean2 <- season_part_clean2 %>% 
  unite(year_season, year:season, sep = "", remove = FALSE, na.rm = TRUE)
```

Checking % of NAs

```{r}
season_part_clean2 %>% 
  summarise_each(funs(100*mean(is.na(.))))
```



```{r}
season_part_clean2 %>% 
  filter(is.na(season)) %>% 
  arrange(desc(year))
```

It appears that for 2021 no season data was captured for wither the  farm team or rally portland, causing us to lose 16 and 43 observations for each respectively when grouping data by season.

```{r}
season_part_clean2 %>% 
  filter(is.na(season)) %>% 
  group_by(program) %>% 
  summarise(count_of_NAs = n())


season_part_clean2 %>% 
  filter(is.na(season)) %>% 
  group_by(program, year) %>% 
  summarise(count_of_NAs = n())
```




As most of the date information is stored in terms of school year (i.e. 20-21), a year column was constructed by extractig a string from the school_year column based on the season (21-22Fall -> 21, as Fall is in the first half of the school year). If no season was given year was determined by the first number in the school year, similar to Fall.

```{r}
season_part_clean2 <- season_part_clean2 %>% 
  rename(school_year  = year) %>% 
  mutate(year = case_when(
    season == "Fall" ~ str_extract(school_year, "[^-]+"),
    season == "Winter" ~ str_extract(school_year, "(?<=-).*"),
    season == "Spring" ~ str_extract(school_year, "(?<=-).*"),
    is.na(season) ~ str_extract(school_year, "[^-]+"),
    .default = as.character(school_year)
  ))
```


```{r}
season_part_clean2 %>% 
  filter(!is.na(season)) %>% 
  distinct(year_season) %>% 
  arrange(desc(year_season))
```

```{r}
season_part_clean2 <- season_part_clean2 %>% 
  filter(!is.na(id))
```

```{r}
season_part_clean2 <- season_part_clean2 %>% 
  rename("contact_id" = "id")
```

```{r}
season_part_clean2
```



```{r}
season_part_clean2 <- season_part_clean2 %>% 
  filter(program == guide_programs_of_int) %>%
  mutate(year_half = case_when((season == "Winter" | season == "Spring") ~1,
                               (season == "Summer" | season == "Fall") ~2,
                               .default = NA))
```


```{r}
season_part_clean2 <- season_part_clean2 %>% 
  group_by(
    contact_id,
    year,
    year_half,
    program
  ) %>% 
  summarize(count = n()) %>% 
  pivot_wider(names_from = program, values_from = count, values_fill = list(count = 0))
```

```{r}
season_part_clean2 %>% 
  filter((year_half == 1) & (Camp == 1))
```



```{r}
season_part_clean2 <- season_part_clean2 %>% 
  mutate(year = (as.numeric(year)+2000)) %>% 
    filter(year >= min_year)
```


```{r}
season_part_clean2
```

```{r}
biannual_activity_count <- biannual_activity_count %>% 
  select('contact_id', 'year', 'year_half', 'fitness_visits', 'squash_visits', 'volworkshift_visits',
                                                'cafestudy_visits', 'event_visits')

season_part_clean2$contact_id <- as.character(season_part_clean2$contact_id)
```

```{r}
biannual_full_activity_count <- biannual_activity_count %>% 
  full_join(season_part_clean2, by=c('contact_id', 'year', 'year_half')) %>% 
  mutate(across(everything(), ~replace(., which(is.na(.)), 0)))
```

```{r}
biannual_full_activity_count
```

```{r}
toc_cleaned_v3
```


```{r}
toc_cleaned_v3$contact_id <- as.character(toc_cleaned_v3$contact_id)

org_a <- biannual_full_activity_count %>% 
  left_join(toc_cleaned_v3, by = 'contact_id')
```


```{r}
names(org_a)
```

```{r}
org_a <- org_a %>% 
  select(-c(toc_rally_portland:farm_team_latest_year))
```

```{r}
org_a <- org_a %>% 
    mutate(date_of_birth = case_when(
    date_of_birth > year(today()) ~ NA,
    .default = date_of_birth
  )) %>% 
  mutate(
    age = (year(today()) - date_of_birth)
  )
```


```{r}
org_a <- org_a %>% 
  mutate(
    org_ipad_event = case_when(event_visits >= 1 ~ "Yes", .default = "No"),
    org_ipad_squash = case_when(squash_visits >= 1 ~ "Yes", .default = "No"),
    org_ipad_fitness = case_when(fitness_visits >= 1 ~ "Yes", .default = "No"),
    org_ipad_volunteer = case_when(volworkshift_visits >= 1 ~ "Yes", .default = "No"),
    org_ipad_cafe = case_when(cafestudy_visits >= 1 ~ "Yes", .default = "No"),
    org_record_rp = case_when(RP >= 1 ~ "Yes", .default = "No"),
    org_record_camp = case_when(Camp >= 1 ~ "Yes", .default = "No"),
    org_record_farm = case_when("Farm Team" >= 1 ~ "Yes", .default = "No")
  )
```

```{r}
org_a %>% 
  filter((year_half == 2) & (Camp ==1))
```


```{r}
org_a
```

```{r}
org_a$equity_milestone_date <- dmy(org_a$equity_milestone_date)

org_a$cohesion_milestone_date <- dmy(org_a$cohesion_milestone_date)
```

```{r}
org_a
```



```{r}
org_a <- org_a %>% 
  mutate(
    equity_met_year_half = case_when(
      (month(equity_milestone_date) >= 1 & month(equity_milestone_date) <= 6) ~ 1,
      (month(equity_milestone_date) >= 7 & month(equity_milestone_date) <= 12) ~ 2,
      .default = NA
    ),
    cohesion_met_year_half = case_when(
      (month(cohesion_milestone_date) >= 1 & month(cohesion_milestone_date) <= 6) ~ 1,
      (month(cohesion_milestone_date) >= 7 & month(cohesion_milestone_date) <= 12) ~ 2,
      .default = NA
    ),
    equity_met = case_when(((year(equity_milestone_date) == year) & (equity_met_year_half == year_half)) ~ "Yes",
                           .default = "No"),
    cohesion_met = case_when(((year(cohesion_milestone_date) == year) & (cohesion_met_year_half == year_half)) ~ "Yes",
                           .default = "No")
    )
```


```{r}
org_a
```


```{r}
org_a %>% 
  filter(year == 2021)
```

```{r}
org_a['guided_access_milestone'] <- guided_access_milestone_goal
org_a['sg_access_milestone'] <- sg_access_milestone_goal
org_a['equity_milestone_goal'] <- equity_milestone_goal
org_a['cohesion_milestone_goal'] <- cohesion_milestone_goal
```

```{r}
org_a <- org_a %>% 
    mutate(country_of_birth = replace(country_of_birth, country_of_birth == "US", "United States"),
           country_of_birth = replace(country_of_birth, country_of_birth == "USA", "United States"))
```


```{r}
Org_tableau_ready <- org_a
```


```{r}
Org_tableau_ready
```


```{r}
Org_tableau_ready %>% 
  filter((year_half == 1) & (Camp == 1))
```



```{r}
Org_tableau_ready

TOC_tableau_ready

ipad_tableau_ready
```




```{r}
Org_tableau_ready %>% write_csv(Ogranizational_file_out)

TOC_tableau_ready %>% write_csv(TOC_file_out)

ipad_tableau_ready %>% write_csv(iPad_file_out)
```


















